Trauma treatment delay

### 2023-10-31 manuscriptlongversion.Rmd
flowchart

>>>>

Out of the 11,864, 5,282 patients were not screened for ofi, which
excludes them from the study. Out of the remaining 6,582 patients, 4,775
patients had missing data in one or more of the analysed parameters,
which led to exclusion from the study.

In the remaining group of 1,835 patients who have been screened for ofi
and have data registered in all parameters examined for the study, 28
patients were found to have received delayed treatment during their stay
at the hospital.

```{r}
library(Gmisc, quietly = TRUE)
library(glue)
library(htmlTable)
library(grid)
library(magrittr)
library(gtsummary)

treated <- boxGrob(glue("Treated at KS between 2012 and 2022",
                           "n = {pop}",
                           pop = txtInt(11864),
                           .sep = "\n"))
screened <- boxGrob(glue("Screened for ofi",
                         "n = {pop}",
                         pop = txtInt(6582),
                         .sep = "\n"))
included <- boxGrob(glue("Included in study",
                         "n = {incl}",
                         incl = txtInt(1835),
                         .sep = "\n"))
delay <- boxGrob(glue("Delay in treatment",
                      "n = {recr}",
                      recr = txtInt(28),
                      .sep = "\n"))

no_delay <- boxGrob(glue("No delay in treatment",
                      "n = {recr}",
                      recr = txtInt(1807),
                      .sep = "\n"))

not_screened <- boxGrob(glue("Not screened for ofi",
                             "n = {recr}",
                             recr = txtInt(11864-6582),
                             .sep = "\n"))

missing_data <- boxGrob(glue("Missing data",
                             "n = {recr}",
                             recr = txtInt(6582-1807),
                             .sep = "\n"))
grid.newpage()
vert <- spreadVertical(treated = treated,
                       screened = screened,
                       included = included,
                       grps = delay)
grps <- alignVertical(reference = vert$grps,
                      delay, no_delay) %>%
  spreadHorizontal()
vert$grps <- NULL

not_screened <- moveBox(not_screened,
                    x = .85,
                    y = .77,)

missing_data <- moveBox(missing_data,
                    x = .85,
                    y = .5,)

for (i in 1:(length(vert) - 1)) {
  connectGrob(vert[[i]], vert[[i + 1]], type = "vert") %>%
    print
}
connectGrob(vert$included, grps[[1]], type = "N")
connectGrob(vert$included, grps[[2]], type = "N")
connectGrob(vert$treated, not_screened, type = "L")
connectGrob(vert$screened, missing_data, type = "L")

# Print boxes
vert
grps
not_screened
missing_data
